ML model comparison

### 2020-10-03 src/s_ml_comparison.Rmd
Update s_ml_comparison.Rmd

Looking into rf performance on 8 schools model more closely
```{r}
x <- x_cp
x <- split_data(x)

@@

x[ , , 9] %>%
  as.data.frame() %>%
  mutate(iter=seq(1,1000,1)) %>%
  melt(id.vars="iter") %>%
  ggplot(aes(x=value, fill=as.factor(variable))) +
  stat_density(position="identity", alpha=0.2)

tibble(var1=testing_data$V1, var2=testing_data$V9, chain=plda) %>% 
  ggplot(aes(x=var1, y=var2, colour=as.factor(chain))) +
  geom_jitter()
```

@@

# calculate R* from gbm and rf
x <- array(dim=c(nrow(x1), 2, ncol(x1)))
x[, 1, ] <- x1
x[, 2, ] <- x2
r_star(x, split_chains = T)

>>>>

Looking into rf performance on 8 schools model more closely
```{r}
x <- x_ncp
x <- split_data(x)

@@

# x[ , , 9] %>%
#   as.data.frame() %>%
#   mutate(iter=seq(1,1000,1)) %>%
#   melt(id.vars="iter") %>%
#   ggplot(aes(x=value, fill=as.factor(variable))) +
#   stat_density(position="identity", alpha=0.2)

tibble(var1=testing_data$V6, var2=testing_data$V10, chain=plda) %>% 
  ggplot(aes(x=var1, y=var2, colour=as.factor(chain))) +
  geom_jitter()
```

@@

# calculate R* from gbm and rf
x <- array(dim=c(nrow(x1), 2, ncol(x1)))
x[, 1, ] <- x1
x[, 2, ] <- x2
r_star(x, split_chains = T)
tmp <- monitor(x)
